Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
added the results section

```
@fig-support-state

@@

```
@fig-support-age

@@

```
@fig-support-sex

>>>>

```
@fig-support-state
In @fig-support-state we see the percentage of the votes for Biden/Democratic party. This graph uses the data we
collected after the post-stratification. Here, the red dots on the graph represent the voting percentage and the red
lines are the error bars. The black vertical line with dashes indicates the line of proportion. Here, it is the equal
split between support for Biden and support for the opposing candidate, Trump.

The states that have points to the left of the black vertical line are the states voting for Trump,
and the states on the right are voting for Biden. We see that the majority of the votes for the democratic party
are found from the Northeast,Midwest  and the West Coast states. For example, the difference in votes for Biden
between Oklahoma and New Mexico is more than 50%, but states like Oregon and Maine are neutral in terms of voting
for either parties.

@@

```
@fig-support-age
In @fig-support-age, we used the data to find the proportion of the voters categorized by age, who would vote for the
Democratic party. We found a pattern that the group of youngest voters and the group of the senior citizen votes are
more likely to vote for the Democratic Party(Biden).

We see that 45% of the individuals from age group 18-29 are voting
for biden as well as 50% of the individuals from the age group of 60+ years. Meanwhile, only 35% of people in the age
group of 45-59 are voting for Biden. Hence, in this graph we see the trend that people of ages from 30-59 are less likely
to vote for the democratic party.

@@

```
@fig-support-sex
@fig-support-sex shows the proportion of Female voters that would vote for the Democratic Party as compared to the Male
voters. We see a 10% difference in the proportion. Here, we see that Women are 10% more likely to vote
